\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-02-04 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
NystrupEtAl2020 corrected

The past decade has seen rapid development in methodologies for forecasting time series that follow a hierarchical aggregation structure. Of particular prominence have been \emph{forecast reconciliation} methods involving two steps: first separate forecasts are produced for all series, then these are adjusted to ensure coherence with aggregation constraints. Forecast reconciliation has mostly been formulated using a regression model {\color{blue} that admits a generalised least squares (GLS) solution}, see \citet{Hyndman2011} and \citet{WicEtAl2019} for examples. {\color{blue} Alternatively, \cite{VanErven2015a} and \cite{NysEtAl2019} arrive at a GLS solution by formulating reconciliation as an optimisation problem}.  The regression setup can be counter-intuitive since a vector comprised of forecasts from different time series models is also assumed to be the dependent variable in a regression model. In this paper, we eschew a regression interpretation in favour of a novel, geometric understanding of forecast reconciliation. This allows us to develop novel proofs and a clearer understanding of the interplay between {\color{blue} objective functions, loss functions, }forecast bias and reconciliation methods.

>>>>

The past decade has seen rapid development in methodologies for forecasting time series that follow a hierarchical aggregation structure. Of particular prominence have been \emph{forecast reconciliation} methods involving two steps: first separate forecasts are produced for all series, then these are adjusted to ensure coherence with aggregation constraints. Forecast reconciliation has mostly been formulated using a regression model {\color{blue} that admits a generalised least squares (GLS) solution}, see \citet{Hyndman2011} and \citet{WicEtAl2019} for examples. {\color{blue} Alternatively, \cite{VanErven2015a} and \cite{NysEtAl2020} arrive at a GLS solution by formulating reconciliation as an optimisation problem}.  The regression setup can be counter-intuitive since a vector comprised of forecasts from different time series models is also assumed to be the dependent variable in a regression model. In this paper, we eschew a regression interpretation in favour of a novel, geometric understanding of forecast reconciliation. This allows us to develop novel proofs and a clearer understanding of the interplay between {\color{blue} objective functions, loss functions, }forecast bias and reconciliation methods.
